---
title: "ETC5513_Assignment1"
author: Chenghuiyu Fan
format: 
    html: 
        toc: true
    pdf:
        toc: true
---

```{r}
#| echo: false
#| message: false
#| warnings: false
library(tidyverse)
library(here)
library(knitr)
```
## Introduction section 
As a Head of Marketing for an online retailer, understanding the relationship between marketing investment and return is critical for our company. Over the last quarter, a new personalised marketing campaign had been used to know how much marketing inventment contacting individual customers. The purpose of this report is to provide data support for the company's future decisions.

## Introduction section 
In this assignment, I will focus on the relationship between “marketing_spend" and "purchase_amount" which can help me to answer the question: did higher marketing spend per customer lead to higher purchase amounts?
And then, I will focus on the differences between different kinds of customers, and get the conclusion of whether different types of customers have different prices?

## Research Question section
The data set records the number of visits to the product and the amount of consumption by different kinds of customers under different marketing investments.

```{r}
#| echo: false
campaign_record <- read.csv(here::here("data", "36427462_Chenghuiyu Fan.csv"))

record_clean <- campaign_record |>
    filter(!is.na(purchase_amount))
    
record_lm <- lm(purchase_amount ~ marketing_spend, data = record_clean)
summary(record_lm)
